---
title: "Topic Gn"
author: "Abhiram Jois"
date: "2025-02-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jsonlite)
library(tidytext)
library(tibble)
library(dplyr)
```

# Read Json file with all the data
```{r}
json_data <- fromJSON("data/allvideos_cleaned.json")
names(json_data)
```

# Tibble for title and desc
```{r}
agt_title <- tibble(title = json_data$Title)
agt_desc <- tibble(
  id = 1:length(json_data$Description),  # Serial numbers
  desc = json_data$Description                      # Descriptions
)
agt_title
agt_desc
```
# Removing stop words for Descriptions
```{r}
agt_desc <- agt_desc %>% 
  unnest_tokens(word, desc) %>% 
  anti_join(stop_words)

agt_desc
```
# Removing stop words for Title
```{r}
agt_title <- agt_title %>% 
  unnest_tokens(word, title) %>% 
  anti_join(stop_words)

agt_title
```


# Sorting words
```{r}
agt_desc %>%
  count(word, sort = TRUE)
```

# Custom stop words
```{r}
my_stopwords <- tibble(word = c(as.character(1:10), "toys", "http", "www.arvindguptatoys.com", "toy", "ashok", "dubbed", "kannada", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", 
  "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "1000", "200", "13", "180", "245", "300",
  "21", "22", "23", "24", "25", "26", "27", "28", "29", "30", 
  "31", "32", "33", "34", "35", "36", "37", "38", "39", "40", 
  "41", "42", "43", "44", "45", "46", "47", "48", "49", "50", 
  "51", "52", "53", "54", "55", "56", "57", "58", "59", "60", 
  "61", "62", "63", "64", "65", "66", "67", "68", "69", "70", 
  "71", "72", "73", "74", "75", "76", "77", "78", "79", "80", 
  "81", "82", "83", "84", "85", "86", "87", "88", "89", "90", 
  "91", "92", "93", "94", "95", "96", "97", "98", "99", "100", "cm", "arvind", "gupta", "credits", "mane", "hiremath", "jyoti", "shivaji", "jain", "manish", "pradnya", "pujari", "vidula", "mhaiskar", "arvindguptatoys.com", "nanawaty", "nanavati", "pk","it's"))

agt_desc <- agt_desc %>% anti_join(my_stopwords)
```
# Identifying pairs

```{r}
library(widyr)
title_word_pairs <- agt_desc %>% 
  pairwise_count(word, id, sort = TRUE)

title_word_pairs
```

# Graph of word pairs
```{r}
library(ggplot2)
library(igraph)
library(ggraph)

set.seed(1234)
title_word_pairs %>%
  filter(n >= 30) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "cyan4") +
  geom_node_point(size = 1) +
  geom_node_text(aes(label = name), repel = TRUE, 
                 point.padding = unit(0.2, "lines")) +
  theme_void()
```

# TF-IDF assign
```{r}
desc_tf_idf <- agt_desc %>% 
  count(id, word, sort = TRUE) %>%
  bind_tf_idf(word, id, n)

desc_tf_idf %>% 
  arrange(-tf_idf)
```

# Generating word counts
```{r}
word_counts <- agt_desc %>%
  count(id, word, sort = TRUE) %>%
  ungroup()

word_counts
```

# Document Matrix
```{r}
library(tm)
desc_dtm <- word_counts %>% cast_dtm(id, word, n)
desc_dtm
```

# Topic modeling
```{r}
library(topicmodels)

# be aware that running this model is time intensive
desc_lda <- LDA(desc_dtm, k = 10, control = list(seed = 1234))
desc_lda

#desc_lda_7 <- LDA(desc_dtm, k = 7, control = list(seed = 1234))
#desc_lda_7
```

# Visualizing the topics
```{r}
library(ggplot2)
tidy_lda <- tidy(desc_lda)

top_terms <- tidy_lda %>%
  group_by(topic) %>%
  slice_max(beta, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  arrange(topic, -beta)

p <- top_terms %>%
        mutate(term = reorder_within(term, beta, topic)) %>%
        group_by(topic, term) %>%    
        arrange(desc(beta)) %>%  
        ungroup() %>%
        ggplot(aes(beta, term, fill = as.factor(topic))) +
        geom_col(show.legend = FALSE) +
        scale_y_reordered() +
        labs(title = "Topics from descriptions of Arvindguptatoys",
             x = expression(beta), y = NULL) +
        facet_wrap(~ topic, ncol = 4, scales = "free")

#ggsave("AGT_Topics_12.png", plot = p, width = 10, height = 12, dpi = 300)
```

# Distribution of topics in descriptions
```{r}
lda_gamma <- tidy(desc_lda, matrix = "gamma")
lda_gamma

ggplot(lda_gamma, aes(gamma)) +
  geom_histogram(alpha = 0.8) +
  scale_y_log10() +
  labs(title = "Distribution of probabilities for all topics",
       y = "Number of documents", x = expression(gamma))

plot_desc <-  ggplot(lda_gamma, aes(gamma, fill = as.factor(topic))) +
            geom_histogram(alpha = 0.8, show.legend = FALSE) +
            facet_wrap(~ topic, ncol = 4) +
            scale_y_log10() +
            labs(title = "Distribution of probability for each topic",
                 y = "Number of documents", x = expression(gamma))

#ggsave("AGT_Distribution_12.png", plot = plot_desc, width = 10, height = 12, dpi = 300)
```

# Assigning a dominant topic to each description
```{r}
desc_topics <- tidy(desc_lda, matrix = "gamma") %>%
  mutate(id = as.integer(document)) %>%  # Convert document ID to integer
  group_by(id) %>%
  filter(gamma == max(gamma, na.rm = TRUE)) %>%  # Select the dominant topic
  slice(1) %>%  # In case of ties, pick the first one
  ungroup() %>%
  rename(topic_probability = gamma)  # Rename for clarity

# Check the number of unique IDs
# desc_topics %>% count(id)


# Get the words contributing to each topic
words_with_topics <- tidy(desc_lda) %>%
  rename(word = term) %>%  # Rename 'term' to 'word'
  inner_join(agt_desc, by = "word")  # Join with words from descriptions

# Link descriptions to topics and contributing words
desc_with_words <- desc_topics %>%
  inner_join(words_with_topics, by = c("id", "topic")) %>%
  select(id, topic, word, beta, topic_probability) %>%
  arrange(id, desc(beta))  # Sort by description ID and word relevance

# Save the results
#write.csv(desc_with_words, "description_topics.csv", row.names = FALSE)

# View first few rows
desc_with_words
```
# Visualizing dominant topics
```{r}
library(ggplot2)
library(dplyr)

# Get the number of unique IDs
num_ids <- n_distinct(desc_topics$id)

# Determine grid size (closest square)
grid_size <- ceiling(sqrt(num_ids))

# Assign X, Y positions for the grid
desc_topics <- desc_topics %>%
  mutate(
    row = (row_number() - 1) %/% grid_size + 1,  # Compute row index
    col = (row_number() - 1) %% grid_size + 1    # Compute column index
  )

# Plot the square grid
ggplot(desc_topics, aes(x = col, y = -row, fill = factor(topic))) +
  geom_tile(color = "white") +  # Create grid squares
  scale_fill_viridis_d() +  # Use a color scale for topics
  theme_minimal() +
  labs(title = "Descriptions Topics Grid",
       x = "Column", y = "Row",
       fill = "Topic") +
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(),
        panel.grid = element_blank())
```

# Putting things together
```{r}
# Extract descriptions and create an ID column
descriptions_tibble <- tibble(
  id = 1:length(json_data$Description),  # Serial numbers
  desc = json_data$Description                      # Descriptions
)

# Check if IDs align before merging
print(head(descriptions_tibble))
print(head(desc_with_words))

# Merge descriptions with existing topic-word data
final_table <- desc_with_words %>%
  group_by(id, topic) %>%
  summarise(
    Words = paste(unique(word), collapse = ", "),  # Combine contributing words
    .groups = "drop"
  ) %>%
  left_join(descriptions_tibble, by = "id") %>%  # Merge descriptions
  rename(
    ID = id,
    Description = desc,
    Topic = topic
  )

# View final table
head(final_table)

```
# Topic and words list
```{r}
# Select top 10 **unique** words per topic based on `beta` and `topic_probability`
topic_word_list <- desc_with_words %>%
  group_by(topic, word) %>%  
  summarise(max_beta = max(beta), .groups = "drop") %>%  # Get max beta for each word
  arrange(topic, desc(max_beta)) %>%  # Sort words by topic and highest beta
  group_by(topic) %>%
  slice_head(n = 20) %>%  # Select top 10 words per topic
  summarise(
    Words = paste(word, collapse = ", "),  # Combine words into a single string
    .groups = "drop"
  )

# View the result
print(topic_word_list)
```
# Exprt topic and word list as csv
```{r}
#write.csv(topic_word_list, "topic_word_list_12.csv", row.names = FALSE)
```

# Import categories
```{r}
library(readr)
categories <- read_csv("data/categories.csv")

# Merge the tables based on 'topic'
merged_table <- merge(categories, topic_word_list, by = "topic")

# Reorder columns
merged_table <- merged_table[, c("topic", "category", "Words")]

# Rename columns for consistency (if needed)
colnames(merged_table) <- c("Topic", "Category", "Words")

# View the result
merged_table
```

# Merging categories
```{r}
# Merge final_table with merged_table on 'Topic' to get the 'Category' column
categories_included <- merge(final_table, merged_table[, c("Topic", "Category")], by = "Topic", all.x = TRUE)

# Reorder columns to match desired order
categories_included <- categories_included[, c("ID", "Topic", "Category", "Description", "Words")]

# View the first few rows
categories_included <- categories_included[order(categories_included$ID), ]

categories_included
```

# Full data with categories
```{r}
# Merge the two data frames based on Description
full_dataset <- merge(categories_included, json_data, by = "Description", all.x = TRUE)

# Reorder the columns
full_dataset <- full_dataset[, c("ID", "Title", "Topic", "Category", "URL", "Description", 
                                 "Words", "Duration", "YouTube Title", "Video Path")]

# Arrange by ID
full_dataset <- full_dataset[order(full_dataset$ID), ]

# View the first few rows
full_dataset
```

# Write to csv
```{r}
write.csv(full_dataset, "full_dataset_10.csv", row.names = FALSE)
```

